\cvsection{Education}
\cvedu{BSc -- ML and Data Science}{University of Copenhagen (DIKU)}{2020 -- 2022}{Copenhagen, Denmark}
\cvedu{MSc -- Software Development}{IT University of Copenhagen}{2016 -- 2018}{Copenhagen, Denmark}
\cvedu{Exchange}{Auckland University of Technology}{2017}{Auckland, New Zealand}
\cvedu{BSc -- Software Development}{IT University of Copenhagen}{2013 -- 2016}{Copenhagen, Denmark}
% \cvachievement{\faTrophy}{}{Received accolades at Atos for Best Performance in team.}
% \cvachievement{\faTrophy}{}{Received Best Debut Award at Atos. }
% %\divider
% \cvachievement{\faInstitution}{}{Won 2nd Consolation Prize for paper presented on Cognitive Radio Networks.}
% %\divider
% \cvachievement{\faGraduationCap}{}{Got Selected in "Exclusive Scholar Program" during undergrad.}
% %\divider
% \cvachievement{\faDollar}{}{Awarded with Narotam Sekhsaria Foundation Scholarship}
%\cvsection{Strengths}

%\cvtag{Hard-working (18/24)} 
%\cvtag{Persuasive}
%\cvtag{Motivator \& Leader}

%\divider\smallskip

%\cvtag{UX}
%\cvtag{Mobile Devices \& Applications}
%\cvtag{Product Management \& Marketing}


%\divider

%\cvevent{B.S.\ in Symbolic Systems}{Stanford University}{Sept 1993 -- June 1997}{}

\cvsection{Personal Projects}
\cvproject{Sala (2018)}
\begin{itemize}
  \item A web app that makes it possible for multiple people online to watch the
  same video while the video player stays synchronized.
  \item The purpose was to learn
  \begin{itemize}
    \item React's functional components (at the time in beta) and how
    it compares to class components and
    \item how Elixir (OTP) and Phoenix can be used to built fault tolerant
    systems to survive unexpected crashes.
  \end{itemize}
\end{itemize}
\cvproject{Cryptomon (2018)}
\begin{itemize}
  \item The project is a simple ``\textbf{crypto} portfolio \textbf{mon}itor''
  to keep track of a user's investments.
  \item I am interested in both web development and functional programming. I
  wanted to see how they could be combined by using Reason and ReasonReact.
\end{itemize}
\smallskip
\smallskip
\cvproject{ShiftPlanning (2017)}
\begin{itemize}
  \item At ITU there is a student driven coffee bar. They need a planning system
  for shifts, so together with some friends, I helped develop such a system.
  \item My responsibility was the web app, written in React and Redux. I learned
  to use the right tool for the right job, as Redux was overkill for this
  project.
\end{itemize}
\smallskip
\smallskip
\cvproject{fourchan-kit (2014)}
\begin{itemize}
  \item My first end-to-end project, a Ruby gem that interacts with the 4chan
  API. A binary is included to download threads, pictures and more.
  \item I learned a lot about how to test, write developer documentation, and
  develop an API for a library.
\end{itemize}
